---
output: html_document
editor_options: 
  chunk_output_type: inline
---




# Set up
```{r Packages}
# To clear your environment 
remove(list = ls())

library(readxl)
library(tidyverse)
library(dplyr)
library(proj4)
library(stringr)
library(scales)
library(lubridate)

## data describe 
library(summarytools)

library(sf)
library(maps)
library(mapdata)

library(RColorBrewer)
library(viridis)
# devtools::install_github("jaredhuling/jcolors")
library(jcolors)
library(scico) ## colors
```


```{r Dirs}
## revision
rr <- 'R1' ## 1st revision for RSE

today <- format(Sys.time(), "%Y%m%d"); print(today)



### Set work dir ----------------------------------------------------------
path <- rstudioapi::getSourceEditorContext()$path
dir  <- dirname(rstudioapi::getSourceEditorContext()$path); dir
dirname(dir)        ## go to parent dir
setwd(dirname(dir) %>% dirname()) ## set this parent dir as root dir
getwd()


dir.root   <- dirname(dir); dir.root
dir.fig    <- paste0(dirname(dir), '/figures/'); dir.fig


### keep more decimals 
options(digits = 15)
options(pillar.sigfig = 15)

```



```{r Shapefile, include=FALSE}
bg_transparent <- 
  theme(
    panel.background = element_rect(fill = "transparent"),             # bg of the panel
    plot.background  = element_rect(fill = "transparent", color = NA), # bg of the plot
    # panel.grid.major = element_blank(), # get rid of major grid
    panel.grid.minor = element_blank(), # get rid of minor grid
    legend.background = element_rect(fill = "transparent"),    # get rid of legend bg
    # legend.box.background = element_rect(fill = "transparent"), # get rid of legend panel bg,
    legend.box.background = element_blank()
  )

shp <- map_data('usa') ## world
head(shp)
```


# Data import

## - All DO data for GEE
  - 1. DO profile data
  - 2. location table for extracting spectral data in GEE
  
```{r paged.print=FALSE}
yr_ini <- 2000

### load cleaned data ------------------------------------------------------------
ls <- list.files(path = dirname(dir) %>% dirname(), pattern = "^DO_Integrated_sf_sp_final_2000_", recursive = T, full.names = T)
print(ls)
# fname <- paste0(dir.output, 'DO_Integrated_sf_sp_final_2000_2019.RData'); fname
# fname <- paste0(dir.output, 'DO_Integrated_sf_sp_final_2000_2021.RData'); fname
fname <- ls[2]; fname

load(fname)
names(df_final)

### 1. DO profile data --> 
df_final_do <- df_final %>%
  dplyr::select(YEID, Year, Date, DO, Depth, Temp, Salin, Source, lat, lon) %>% 
  dplyr::mutate(Date = as.Date(Date)) 

remove_overlap <- df_final_do %>%
  ## remove duplicated points ---------------------------------------------------------
  dplyr::mutate(lat1 = round(lat, digits = 4), lon1 = round(lon, digits = 4), len = nchar(YEID)) %>%
  dplyr::group_by(Year) %>%
  arrange(Date, Source, len) %>%
  dplyr::distinct(Date, Source, lat1, lon1, .keep_all = T) %>%
  dplyr::distinct(YEID, Year) %>%
  as.data.frame()


df_final_do <- df_final_do %>%
  dplyr::filter(YEID %in% unique(remove_overlap$YEID))


### 2. location table (NOT SURE WE SHOULD INCLUDE hypoxia watch DATA, perhaps NOT at this moment)
df_final_pt <- sp_final %>%
  dplyr::filter(Year >= yr_ini) %>%
  dplyr::select(YEID, Date, Year, lat, lon) %>%
  distinct(YEID, .keep_all = T) %>%
  dplyr::mutate(Date = as.Date(Date))%>%
  dplyr::mutate(id = row.names(.))

### how many sampling locations in each year?
df_final_pt %>%
  ungroup() %>% dplyr::group_by(Year) %>% tally() %>% as.data.frame()

### point to sf
projcrs <- "+proj=longlat +datum=WGS84 +no_defs +ellps=WGS84 +towgs84=0,0,0"
df_final_pt_sf <- st_as_sf(df_final_pt, coords = c("lon", "lat"), crs = projcrs)
# ggplot() + geom_sf(data = df_final_pt_sf, col = "red", size = 1) + theme_bw()
```



## - Save to RData
```{r include=FALSE}
yrmin <- min(year(df_final_do$Date), na.rm = T); yrmin
yrmax <- max(year(df_final_do$Date), na.rm = T); yrmax

### write to file ---------------------------
fname <- paste0(dirname(dir), '/data/data_for_gee/sample_', yrmin, '_', yrmax, '_DO.xlsx'); fname  ### xlsx can be smaller than csv file
writexl::write_xlsx(x = df_final_do, path = fname)
# fname <- paste0(dirname(dir), '/data/data_for_gee/sample_2000_2019_DO.csv'); fname 
# write.csv(x = df_final_do, file = fname, row.names = F)

fname <- paste0(dirname(dir), '/data/data_for_gee/sample_', yrmin, '_', yrmax, '_locations.csv'); fname
# writexl::write_xlsx(x = df2014_pt, path = fname)
write.csv(x = df_final_pt, file = fname, row.names = F)

fname <- paste0(dirname(dir), '/data/data_for_gee/sample_', yrmin, '_', yrmax, '_locations.shp'); fname
st_write(obj = df_final_pt_sf, dsn = fname, delete_layer = TRUE, delete_dsn = T) # overwrites
```




```{r - Data for Sam, include=FALSE}
names(df_final)
yr <- 2014

### sampling data for 2014 --------------------
df2014 <- df_final %>%
  ungroup() %>%
  dplyr::filter(YEID %in% unique(remove_overlap$YEID)) %>%
  dplyr::filter(Year == yr) %>%
  # dplyr::filter(nchar(YEID) < 10) %>%
  dplyr::select(YEID, Year, Date, DO, Depth, Temp, Salin, Source, lat, lon, Depth_dem) %>% 
  dplyr::mutate(Date = as.Date(Date)) %>%
  dplyr::mutate(mm = month(Date)) %>% 
  dplyr::filter(mm <=9, Depth <=80) %>% dplyr::select(-mm)

# dfSummary(df2014)
names(df2014)


### sampling locations that will be used for extracting Spectral_Value from images
df2014_pt <- df2014 %>%
  distinct(YEID, Date, lat, .keep_all = T) %>%
  dplyr::select(YEID, Date, Year, lat, lon) %>%
  arrange(YEID, Date, lat, lon) %>%
  dplyr::mutate(id = row.names(.))

projcrs <- "+proj=longlat +datum=WGS84 +no_defs +ellps=WGS84 +towgs84=0,0,0"
df2014_sf  <- st_as_sf(df2014_pt, coords = c("lon", "lat"), crs = projcrs)
df2014_sf2 <- st_as_sf(x = df2014_pt %>% dplyr::filter(nchar(YEID)<10), coords = c("lon", "lat"), crs = projcrs)
ggplot() + geom_sf() + 
  geom_sf(data = df2014_sf,  col = "red",   size = 3, alpha=0.6) + 
  geom_sf(data = df2014_sf2, col = "black", size = 3, alpha=0.6) + 
  theme_bw()



### write to file under the original dir ---------------------------
getwd()

fname <- paste0(dirname(dir), '/data/data_for_gee/_for_sam/sample_2014_DO_plusBathymetry3.xlsx'); fname
writexl::write_xlsx(x = df2014, path = fname)

fname <- paste0(dirname(dir), '/data/data_for_gee/_for_sam/sample_2014_locations3.csv'); fname
# writexl::write_xlsx(x = df2014_pt, path = fname)
write.csv(x = df2014_pt, file = fname, row.names = F)

fname <- paste0(dirname(dir), '/data/data_for_gee/_for_sam/sample_2014_locations3.shp'); fname
st_write(obj = df2014_sf, dsn = fname, delete_layer = TRUE) # overwrites



## write to file under the new dir -----------------------------------
fname <- paste0(dirname(dir), '/data/sample_2014_DO_plusBathymetry3.xlsx'); fname
writexl::write_xlsx(x = df2014, path = fname)

fname <- paste0(dirname(dir), './data/sample_waterData3.csv'); fname
readr::write_csv(x = df2014, path = fname)

```



## - Data description

  Figure S2. Sampling date at each sampling location (a) and the distribution of the sampling dates. 

```{r - Fig S2}

require("ggrepel") ## for `geom_text_repel`

do <- df2014


### Fig S2b
(s2b <- 
  do %>% 
    ungroup() %>%
    distinct(YEID, Date, .keep_all = T) %>%
    group_by(YEID, Date) %>% tally() %>%
    as.data.frame() %>%
    ggplot()+
    geom_col(aes(x = Date, y = n)) +
    ggtitle('Number of sampling locations by date in 2014') + 
    ylab('Count') +
    theme_bw()
)
  
  
### Fig S2a
doDmax <- do %>% 
  ungroup() %>%
  group_by(YEID) %>%
  slice(which.max(Depth))

(s2a <- 
  doDmax %>%
    dplyr::mutate(mm = as.factor(paste(month(Date), day(Date), sep = '-')),
                  date= as.numeric(Date)) %>%
    ggplot(aes(x = lon, y = lat, label = mm))+ ## , color = date
    geom_point(aes(fill = DO), size = 3, colour = "NA",
               # alpha = 0.6, 
               shape = 21, show.legend = T) +
    geom_text(aes(color = date),show.legend = F, 
              nudge_y = -0.04,
              nudge_x = 0.15) +
    # scale_color_viridis(option = "D", begin = 0.2, end = 1, direction = -1)+
    # scale_fill_viridis(option = "D", begin = 0, end = 1, direction = -1)+
    scico::scale_color_scico(palette = "roma", direction = -1) +
    scico::scale_fill_scico(palette = "roma") +
    # scale_color_distiller(palette = "Spectral")
    # scale_colour_continuous(trans = 'reverse') +
    ylab('Latitude') + xlab('Longitude') +
    labs(fill = 'DO (mg/l)') +
    ggtitle('Sampling date in 2014') +
    theme_bw() +
    theme(legend.position=c(0.945, 0.19), legend.key.height = unit(0.35, 'cm'),
          legend.background = element_rect(fill='transparent')))
  


ggpubr::ggarrange(s2a, s2b, labels = c('(a)', '(b)'), nrow = 2,
                  font.label = list(color = "black", face = "plain", family = NULL, position = "top"))

fname <- paste0(dir.fig, 'Fig S2_', rr, '.png'); #fname
ggsave(filename = fname, plot = last_plot(), bg = "transparent",
       width = 7, height = 7, units = 'in', dpi = 300)
```



```{r - Fig S3}
## Figure S3. The total number of DO samples in the profile at each sampling location. -------------
do %>% group_by(YEID, lat, lon) %>% tally() %>%
  # dplyr::filter(nchar(YEID) < 10) %>%
  ggplot()+
  geom_text(aes(x = lon, y = lat, label = n, size = n), show.legend = F) +
  ggtitle('Number of samples at each location in 2014') +
  ylab('Latitude') + xlab('Longitude') +
  theme_bw()


# do %>% group_by(YEID, lat, lon) %>% tally() %>%
#   ggplot()+
#   # geom_col(aes(x = YEID, y = n)) +
#   # geom_point(aes(x = lon, y = lat, color = n), size = 1) +
#   geom_text(aes(x = lon, y = lat, label = n)) +
#   # geom_text_repel(aes(x = lon, y = lat, color = n, label = n, )) +
#   theme_bw()

fname <- paste0(dir.fig, 'Fig S3_', rr, '.png'); #fname
ggsave(filename = fname, plot = last_plot(), bg = "transparent",
       width = 7, height = 3.5, units = 'in', dpi = 300)
```



```{r - Fig S4, warning=FALSE}
## Figure S4. DO and water temperature in the profile at different depths. -------------------------
do %>%
  ggplot()+
  geom_point(aes(x = DO, y = -Depth, color = Temp), show.legend = T) +
  facet_wrap(~Date) +
  # scico::scale_color_scico(palette = "roma") +
  scale_color_viridis(option="inferno", direction = 1) +
  geom_vline(xintercept = 2, 'dash') +
  ylab('Sampling depth (m)') + xlab('DO (mg/l)') +
  ggtitle('DO and water temperature at different sampling depth') +
  theme_bw()
fname <- paste0(dir.fig, 'Fig S4_', rr, '.png'); #fname
ggsave(filename = fname, plot = last_plot(), bg = "transparent",
       width = 8, height = 8, units = 'in', dpi = 300)
```





```{r - Other}
## number of samples at each location
do %>% 
  group_by(YEID, lat, lon) %>% tally() %>%
  dplyr::filter(nchar(YEID) < 10) %>%
  as.data.frame() %>%
  ggplot()+
  # geom_violin(mapping = aes(x = 1, y = n)) + 
  geom_histogram(aes(x = n)) +
  xlab('Number of samples at each location') + ylab('Count') +
  theme_bw()


## depths distribution
do %>% 
  dplyr::filter(nchar(YEID) < 10) %>%
  as.data.frame() %>%
  ggplot()+
  # geom_violin(mapping = aes(x = 1, y = n)) + 
  geom_histogram(aes(x = Depth)) +
  ggtitle('Distribution of sampling depth') + 
  theme_bw()
  
library(classInt)
# it <- classIntervals(var = do$DO, n = 10, style = "jenks")
# it$brks

it2 <- classIntervals(var = do$DO, n = 10, style = 'quantile')
it2$brks
```




```{r - Map samples by year & by source}

## 1. sample number stack bar by year ------------------------------------------------------------
size_key = 0.4

sp_final %>% ggplot() + 
  geom_bar(aes(x=Year, fill = Source), position = "stack") + 
  ylab('Number of sampling locations') +
  scale_x_continuous(breaks = seq(min(sp_final$Year), max(sp_final$Year), by = 1))+
  theme_bw()+
  bg_transparent +
  theme(axis.text.x = element_text(angle = 90, hjust = 1,vjust = 0.5),
        # legend.key.size   = unit(size_key, "cm"),
        legend.key.height = unit(size_key, "cm"),
        legend.key.width  = unit(size_key, "cm")) +
  # guides(shape = guide_legend(override.aes = list(size = size_key)), ## change the legend key size
  #        color = guide_legend(override.aes = list(size = size_key)),
  #        fill  = guide_legend(override.aes = list(size = size_key))) +
  theme(legend.position = c(0.1, 0.8)) 

pname <- paste0(dir.fig, 'total_count_sample_bySources1_', rr, '.png'); pname
# ggsave(filename = pname, plot = last_plot(),  bg = "transparent",
#        width = 6, height = 6, units = 'in', dpi = 300)




## 2. sample distribution facet by year ----------------------------------------------------------
ggplot() + 
  # geom_polygon(data = shp, aes(x=long, y = lat, group = group), fill = 'gray90') + 
  # scale_fill_viridis_d(option = "viridis", alpha = 0.6)+
  geom_point(data = sp_final,  # use geom_point, instead of geom_sf
             aes(x = lon, y = lat, color = Source), alpha = 0.9, size = 1.5) +
  # scale_color_brewer(palette = "Dark2") +
  facet_wrap(.~Year)+
  theme_bw() +
  xlab('Longitude') + ylab('Latitude')+
  guides(color = guide_legend(override.aes = list(size=4))) ## enlarge the key size

pname <- paste0(dir.fig, 'map_samp_by year1_', rr, '.png'); pname
# ggsave(filename = pname, plot = last_plot(), 
#        width = 14, height = 8, units = 'in', dpi = 300)




## 3. sample distribution facet by data source ---------------------------------------------------
ggplot() + 
  geom_point(data = sp_final,  # use geom_point, instead of geom_sf
             aes(x = lon, y = lat, color = Year), alpha = 0.5) +
  facet_wrap(.~Source)+
  # scale_color_gradient2(low = 'blue', mid = 'green', high = 'red', midpoint = 2000)+
  scale_color_viridis(option = "D") +
  xlab('Longitude') + ylab('Latitude')+
  theme_bw()
pname <- paste0(dir.fig, 'map_samp_by source2_', rr, '.png'); pname
# ggsave(filename = pname, plot = last_plot(), width = 14, height = 8, units = 'in', dpi = 300)

```






## - Bottom DO 

  do_min:       minimum DO at 3-80m depth across the profile 
  do_depth_max: DO at the max depth (3-80m) across the profile
  do_20m:       DO at  3-20m depth across the profile
  do_50m:       DO at 21-50m depth across the profile
  do_80m:       DO at 51-80m depth across the profile

  * See script - `11_DO1+DO2HypoxiaWatch_DataDesc.Rmd`

```{r}

## here we use data from `telecoupling`
f <- list.files(path = dirname(getwd()), pattern = "^sample_2000_2019_do_bottom\\.xlsx$", full.names = T, recursive = T)
f
if(length(f) > 1) {
  break  ## if there are two or more files found, report error. If only one, then go on. 
} else {
  fname <- f; #fname
}

do_depth_max <- readxl::read_excel(path = f)
```






  Figure S1. Bottom DO levels at each sampling location (dots) and the mean DO levels in each grid (polygon). 
```{r - Fig S1 - spatial grid}
### perhaps to look at several sub-regions, using fishnet?
globe_bb <- matrix(c(-96, 30,  ## left upper
                     -88,  30,   ## right upper
                     -88,  28,   ## right lower
                     -96, 28,  ## left lower
                     -96, 30), byrow = TRUE, ncol = 2) %>%
  list() %>% 
  st_polygon() %>% 
  st_sfc(., crs = 4326)
grid <- st_make_grid(globe_bb, cellsize = c(1/2, 0.5/2),
                           crs = 4326, what = 'polygons') %>%
  st_sf('geometry' = ., data.frame('ID' = 1:length(.))) %>%
  dplyr::mutate(label = ID)
str(grid)
plot(grid)
# st_write(obj = grid, dsn = paste0(dir.root, '/data/grid/grid.shp'))




### point to sf
# projcrs <- "+proj=longlat +datum=WGS84 +no_defs +ellps=WGS84 +towgs84=0,0,0"
projcrs <- 4326
do_depth_max_sf <- do_depth_max %>%
  ungroup() %>%
  dplyr::filter(nchar(YEID) < 10) %>%
  dplyr::filter(Year == 2014) 
do_depth_max_sf <- st_as_sf(do_depth_max_sf, coords = c("lon", "lat"), crs = projcrs)
str(do_depth_max_sf)

ggplot() +
  geom_sf(data = do_depth_max_sf, aes(color = DO)) +
  geom_sf(data = grid, fill = NA, color = 'red', size = 0.1) +
  scico::scale_color_scico(palette = "roma") +
  theme_bw() +
  theme(panel.grid.minor = element_blank(), axis.title = element_blank(),
        legend.position = 'bottom')

fname <- paste0(dir.fig, 'do_bottom_map_2014_', rr, '.png'); fname
# ggsave(filename = fname, plot = last_plot(), width = 7, height = 3, units = 'in', dpi = 300)







### join 'points' and 'polygon' =========================
pts  <- do_depth_max_sf
poly <- grid
pts.poly <- st_join(x = pts, y = poly, join = st_within) 

pts.poly.agg <- pts.poly %>%
  st_drop_geometry() %>%
  group_by(ID) %>%
  summarise(do_mean = mean(DO, rm.na = T))

pts.poly.agg.sf <- merge(grid, pts.poly.agg, by = 'ID', all.x = T)

ggplot() +
  geom_sf(data = pts.poly.agg.sf, aes(fill = do_mean), alpha = 0.5) +
  geom_sf_text(data = pts.poly.agg.sf, aes(label = ID), colour = "red", size = 2) +
  scico::scale_fill_scico(palette = "roma") +
  theme_bw() +
  theme(panel.grid.minor = element_blank(), axis.title = element_blank(),
        legend.position = 'bottom')

fname <- paste0(dir.fig, 'do_bottom_map_2014_agg_', rr, '.png'); fname
# ggsave(filename = fname, plot = last_plot(), width = 7, height = 3, units = 'in', dpi = 300)




ggplot() +
  geom_sf(data = do_depth_max_sf, aes(color = DO), show.legend = T) +
  geom_sf(data = pts.poly.agg.sf, aes(fill = do_mean), alpha = 0.5, show.legend = F) +
  scico::scale_fill_scico(palette = "roma") +
  scico::scale_color_scico(palette = "roma") +
  # guides(fill = guide_legend(title='DO (mg/l)', )) +
  labs(color = "DO (mg/l)") +
  theme_bw() +
  theme(panel.grid.minor = element_blank(), legend.position = 'bottom')

fname <- paste0(dir.fig, 'do_bottom_map_2014_agg_FigS1_', rr, '.png'); fname
ggsave(filename = fname, plot = last_plot(), width = 7, height = 3, units = 'in', dpi = 300)

```




* do_10m
```{r eval=FALSE, include=FALSE}

### do_10m -----------------------------------------------
do_10m <- df_final %>%
  ungroup() %>%
  dplyr::filter(Depth >= 3, Depth <=10) %>%
  group_by(YEID) %>%
  
  ## to see the min, avg, and sd in this depth range
  dplyr::mutate(
    DO = median(DO, na.rm = T),
    n = n()) %>%
  distinct(YEID, DO, .keep_all = T) %>%
  dplyr::select(-n) %>%
  
  ### take the min DO in this depth range
  # slice(which.min(DO)) %>%
  
  as.data.frame()

# fname <- paste0(dirname(dir), '/data/data_for_gee/sample_2000_2019_DO_10m.xlsx'); fname
# writexl::write_xlsx(x = do_10m, path = fname)








### do_20m -----------------------------------------------
do_20m <- df_final %>%
  ungroup() %>%
  dplyr::filter(Depth >= 10, Depth <=20) %>%
  group_by(YEID) %>%
  
  ## to see the min, avg, and sd in this depth range
  # dplyr::mutate(
    # do_20m_min = min(DO, na.rm = T),
    # do_20m_avg = mean(DO, na.rm = T),
    # do_10m_med = median(DO, na.rm = T),
    # do_20m_dev = sd(DO, na.rm = T),
    # n = n()) %>%
  
  ### take the min DO in this depth range
  slice(which.min(DO)) %>%
  as.data.frame()

fname <- paste0(dirname(dir), '/data/data_for_gee/sample_2000_2019_DO_20m.xlsx'); fname  ### xlsx can be smaller than csv file
# writexl::write_xlsx(x = do_20m, path = fname)



### do_50m -----------------------------------------------
do_50m <- df_final %>%
  ungroup() %>%
  dplyr::filter(Depth >= 21, Depth <=50) %>%
  group_by(YEID) %>%
  ### to see the min, avg, and sd in this depth range
  # dplyr::mutate(do_20m_min = min(DO, na.rm = T),
                # do_20m_avg = mean(DO, na.rm = T),
                # do_20m_dev = sd(DO, na.rm = T),
                # n = n()) %>%
  ### take the min DO in this depth range
  slice(which.min(DO)) %>%
  as.data.frame()
do_50m %>%
  ggplot() +
  geom_point(aes(x = Depth, y = DO, color = Source)) +
  theme_bw()



### do_80m -----------------------------------------------
do_80m <- df_final %>%
  ungroup() %>%
  dplyr::filter(Depth >= 51, Depth <=80) %>%
  group_by(YEID) %>%
  ### to see the min, avg, and sd in this depth range
  # dplyr::mutate(do_20m_min = min(DO, na.rm = T),
                # do_20m_avg = mean(DO, na.rm = T),
                # do_20m_dev = sd(DO, na.rm = T),
                # n = n()) %>%
  ### take the min DO in this depth range
  slice(which.min(DO)) %>%
  as.data.frame()
do_80m %>%
  ggplot() +
  geom_point(aes(x = Depth, y = DO, color = Source)) +
  theme_bw()

```




* do_min
```{r eval=FALSE, include=FALSE}
### do_min ------------------------------------------------
do_min <- df_final %>%
  ungroup() %>%
  dplyr::filter(Depth >= 3, Depth <=80) %>%
  group_by(YEID) %>%
  slice(which.min(DO))
length(unique(do_min$YEID))

fname <- paste0(dirname(dir), '/data/data_for_gee/sample_2000_2019_DO_min.xlsx'); fname  ### xlsx can be smaller than csv file
# writexl::write_xlsx(x = do_min, path = fname)



### plot ----------------------------------------------------
do_min %>%
  ungroup() %>%
  dplyr::filter(Year >= 2005) %>%
  group_by(Year) %>%
  tally() %>%
  ggplot(aes(x=Year, y=n, fill = n))+
  geom_col(show.legend = F) +
  geom_text(aes(label = n), hjust = 0.5, vjust = -0.5, size = 3) + 
  theme_bw() +
  # theme_classic() +
  ggtitle('do_min')+ ylab('Number of sampling locations') +
  scale_x_continuous(breaks = seq(2000, max(do_min$Year), 1)) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1),
        # panel.grid.major = element_blank(),
        panel.grid.minor = element_blank())


# dfsummary %>%
#   ungroup() %>%
#   dplyr::filter(Year >= 2000) %>%
#   group_by(Year) %>%
#   tally() %>%
#   ggplot(aes(x=Year, y=n))+
#   geom_col() +
#   geom_text(aes(label = n), hjust = 0.5, vjust = -0.5, size = 2) + 
#   theme_bw() +
#   # theme_classic() +
#   ggtitle('dfsummary')+ ylab('Number of sampling locations') +
#   scale_x_continuous(breaks = seq(2000, 2017, 1)) +
#   theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1),
#         # panel.grid.major = element_blank(),
#         panel.grid.minor = element_blank())
```



