---
title: "Untitled"
author: "Yingjie"
date: "07/22/2021"
output: html_document
editor_options: 
  chunk_output_type: console
---



# Set up
```{r Packages}
# To clear your environment 
# remove(list = ls())

library(readxl)
library(tidyverse)
library(dplyr)
library(proj4)
library(stringr)
library(scales)
library(lubridate)

## data describe 
library(summarytools)

library(sf)
library(maps)
library(mapdata)

library(RColorBrewer)
library(viridis)
# devtools::install_github("jaredhuling/jcolors")
library(jcolors)
library(scico) ## colors

### keep more decimals 
options(digits = 15)
options(pillar.sigfig = 15)
```


```{r Dirs}
### Set work dir ----------------------------------------------------------
path <- rstudioapi::getSourceEditorContext()$path
dir  <- dirname(rstudioapi::getSourceEditorContext()$path); dir
dirname(dir)        ## go to parent dir
setwd(dirname(dir)) ## set this parent dir as root dir
getwd()

### the data dir ----------------------------------------------------------
dir.path <- '../Dead_Zone_telecoupling/data/DO/DO_GOM/DO_Integrated_Matli_NCSU'
setwd(dir.path)
getwd()

dir.root   <- dirname(dir) %>% dirname()
dir.fig    <- paste0(dirname(dir), '/figures/'); dir.fig
dir.output <- './data_cleaned/'

today <- format(Sys.time(), "%Y%m%d"); print(today)
postfix <- 'R2'
```



# Data
## - All DO data for GEE
  - 1. DO profile data
  - 2. location table for extracting spectral data in GEE
```{r}
### load cleaned data ------------------------------------------------------------
fname <- paste0(dir.output, 'DO_Integrated_sf_sp_final_2000_2019.RData');   fname
load(fname)
names(df_final)

### 1. DO profile data --> 
df_final_do <- df_final %>%
  dplyr::select(YEID, Year, Date, DO, Depth, Temp, Salin, Source, lat, lon) %>% 
  dplyr::mutate(Date = as.Date(Date))


### 2. location table (NOT SURE WE SHOULD INCLUDE hypoxia watch DATA, perhaps NOT at this moment)
df_final_pt <- sp_final %>%
  dplyr::filter(Year >= 2000) %>%
  dplyr::select(YEID, Date, Year, lat, lon) %>%
  distinct(YEID, .keep_all = T) %>%
  dplyr::mutate(Date = as.Date(Date))%>%
  dplyr::mutate(id = row.names(.))

### how many sampling locations in each year?
df_final_pt %>%
  ungroup() %>% dplyr::group_by(Year) %>% tally()

### point to sf
projcrs <- "+proj=longlat +datum=WGS84 +no_defs +ellps=WGS84 +towgs84=0,0,0"
df_final_pt_sf <- st_as_sf(df_final_pt, coords = c("lon", "lat"), crs = projcrs)
# ggplot() + geom_sf(data = df_final_pt_sf, col = "red", size = 1) + theme_bw()
```





## - 2014 DO data description
```{r}
names(df_final)

### sampling data for 2014 --------------------
df2014 <- df_final %>%
  dplyr::filter(Year == 2014) %>%
  dplyr::filter(nchar(YEID) < 10) %>%
  dplyr::select(YEID, Year, Date, DO, Depth, Temp, Salin, Source, lat, lon, Depth_dem) %>% 
  dplyr::mutate(Date = as.Date(Date))

# dfSummary(df2014)
names(df2014)


### sampling locations that will be used for extracting Spectral_Value from images
df2014_pt <- df2014 %>%
  distinct(YEID, Date, lat, .keep_all = T) %>%
  dplyr::select(YEID, Date, Year, lat, lon) %>%
  arrange(Date, lat, lon) %>%
  dplyr::mutate(id = row.names(.))

projcrs <- "+proj=longlat +datum=WGS84 +no_defs +ellps=WGS84 +towgs84=0,0,0"
df2014_sf <- st_as_sf(df2014_pt, coords = c("lon", "lat"), crs = projcrs)
# ggplot() + geom_sf() + geom_sf(data = df2014_sf, col = "red", size = 6, alpha=0.6) + theme_bw()
```


  Figure S2. Sampling date at each sampling location (a) and the distribution of the sampling dates. 

```{r - Fig S2}
require("ggrepel") ## for `geom_text_repel`

do <- df2014


### Fig S2b
(s2b <- 
  do %>% 
    ungroup() %>%
    distinct(YEID, Date, .keep_all = T) %>%
    group_by(YEID, Date) %>% tally() %>%
    as.data.frame() %>%
    ggplot()+
    geom_col(aes(x = Date, y = n)) +
    ggtitle('Number of sampling locations by date in 2014') + 
    ylab('Count') +
    theme_bw()
)
  
  
### Fig S2a
doDmax <- do %>% 
  ungroup() %>%
  group_by(YEID) %>%
  slice(which.max(Depth))

(s2a <- 
  doDmax %>%
    dplyr::mutate(mm = as.factor(paste(month(Date), day(Date), sep = '-')),
                  date= as.numeric(Date)) %>%
    ggplot(aes(x = lon, y = lat, label = mm))+ ## , color = date
    geom_point(aes(fill = DO), size = 3, colour = "NA",
               # alpha = 0.6, 
               shape = 21, show.legend = T) +
    geom_text(aes(color = date),show.legend = F, 
              nudge_y = -0.04,
              nudge_x = 0.15) +
    scico::scale_color_scico(palette = "roma", direction = -1) +
    scico::scale_fill_scico(palette = "roma") +
    ylab('Latitude') + xlab('Longitude') +
    labs(fill = 'DO (mg/l)') +
    ggtitle('Sampling date in 2014') +
    theme_bw() +
    theme(legend.position=c(0.945, 0.19), legend.key.height = unit(0.35, 'cm'),
          legend.background = element_rect(fill='transparent')))
  


ggpubr::ggarrange(s2a, s2b, labels = c('(a)', '(b)'), nrow = 2,
                  font.label = list(color = "black", face = "plain", family = NULL, position = "top"))

fname <- paste0(dir.fig, 'Fig S2_', postfix,'.png'); fname
ggsave(filename = fname, plot = last_plot(), bg = "transparent",
       width = 7, height = 7, units = 'in', dpi = 300)
```



```{r - Fig S3}
## Figure S3. The total number of DO samples in the profile at each sampling location. -------------
do %>% group_by(YEID, lat, lon) %>% tally() %>%
  dplyr::filter(nchar(YEID) < 10) %>%
  ggplot()+
  geom_text(aes(x = lon, y = lat, label = n, size = n), show.legend = F) +
  ggtitle('Number of samples at each location in 2014') +
  ylab('Latitude') + xlab('Longitude') +
  theme_bw()


fname <- paste0(dir.fig, 'Fig S3_', postfix,'.png'); fname
ggsave(filename = fname, plot = last_plot(), bg = "transparent",
       width = 7, height = 3.5, units = 'in', dpi = 300)
```



```{r - Fig S4}

## label the points that are defined as "bottom" 
do_isbottom <- do %>%
  group_by(YEID) %>%
  # dplyr::mutate(depth_max = max(Depth, na.rm = T),
  #               is_bottom = ifelse(Depth == depth_max, 'bottom', 'non-bottom')) %>%
  # dplyr::filter(is_bottom != 'non-bottom') %>%
  # dplyr::select(-depth_max) %>%
  as.data.frame()


## Figure S4. DO and water temperature in the profile at different depths. -------------------------
# do %>% ## 1st submission used `do` as input data
do_isbottom %>%  
  dplyr::mutate(label = ifelse(Date == as.Date("2014-05-26"), "Hypoxia", '')) %>%
  ggplot()+
  
  # geom_rect(aes(xmin = -Inf, xmax = 2, ymin = -Inf, ymax = Inf),
  #           fill = "grey", alpha = 0.4, color = "red") +
  annotate(geom = "rect", xmin = -Inf, xmax = 2, ymin = -Inf, ymax = Inf,
           fill = "gray", colour = NA, alpha = 0.5) +
  # annotate(geom = "text",
  #          x = 1, y = -75,
  #          angle = 0, hjust = 0,
  #          aes(label = label)) +
  geom_text(
           x = .5, y = -70,
           angle = 90, color = 'gray50',
           # hjust = 0, 
           aes(label = label)) +
  
  geom_point(aes(x = DO, y = -Depth, color = Temp), show.legend = T) + ## `, shape = is_bottom`
  # facet_wrap(~Date) +                          ## 1st submission used this line 
  # facet_grid(Date ~ is_bottom) +               ## 1st revision used this line
  # facet_wrap(Date ~ is_bottom, ncol = 10) +    ## 1st revision used this line
  facet_wrap(~Date) +                            ## 2nd revision used this line
  
  scale_color_viridis(option="inferno", direction = 1) +
  scale_x_continuous(breaks = c(2, seq(0, 15, 5)), limits = c(0, 17)) + 
  geom_vline(xintercept = 2,   color = "red",  alpha = 0.6) + #linetype = "dotted", 
  geom_hline(yintercept = -50, color = "gray", alpha = 0.7, linetype = "dashed") +
  
 
  
  ylab('Sampling depth (m)') + 
  xlab('DO (mg/l)') +
  ggtitle('DO and water temperature at different sampling depth') +
  theme_bw() +
  theme(panel.grid.minor = element_blank())

fname <- paste0(dir.fig, 'Fig S4_', postfix,'.png'); fname
ggsave(filename = fname, plot = last_plot(), bg = "transparent",
       width = 12, height = 8, units = 'in', dpi = 300)
```






  * Was tring to color the strips by group, but did not work out.
    
    See the following link for future explore. Be caution that there is an error in the code posted on this webpage --> using "strip-t" (correct) instead of "strip_t" (wrong). 
  https://stackoverflow.com/questions/19440069/ggplot2-facet-wrap-strip-color-based-on-variable-in-data-set
  
  * the example data

```{r eval=FALSE, include=FALSE}
d <- data.frame(fruit = rep(c("apple", "orange", "plum", "banana", "pear", "grape")), 
                farm = rep(c(0,1,3,6,9,12), each=6), 
                weight = rnorm(36, 10000, 2500), 
                size=rep(c("small", "large")))

p1 = ggplot(data = d, aes(x = farm, y = weight)) + 
  geom_jitter(position = position_jitter(width = 0.3), 
              aes(color = factor(farm)), size = 2.5, alpha = 1) + 
  facet_wrap(~fruit)

dummy <- ggplot(data = d, aes(x = farm, y = weight))+ facet_wrap(~fruit) + 
  geom_rect(aes(fill=size), xmin=-Inf, xmax=Inf, ymin=-Inf, ymax=Inf) +
  theme_minimal()

library(gtable)

g1 <- ggplotGrob(p1)
g2 <- ggplotGrob(dummy)

gtable_select <- function (x, ...) 
{
  matches <- c(...)
  x$layout <- x$layout[matches, , drop = FALSE]
  x$grobs <- x$grobs[matches]
  x
}

panels <- grepl(pattern="panel", g2$layout$name)
strips <- grepl(pattern="strip-t", g2$layout$name)
g2$layout$t[panels] <- g2$layout$t[panels] - 1
g2$layout$b[panels] <- g2$layout$b[panels] - 1

new_strips <- gtable_select(g2, panels | strips)
grid.newpage()
grid.draw(new_strips)

gtable_stack <- function(g1, g2){
  g1$grobs <- c(g1$grobs, g2$grobs)
  g1$layout <- transform(g1$layout, z= z-max(z), name="g2")
  g1$layout <- rbind(g1$layout, g2$layout)
  g1
}
## ideally you'd remove the old strips, for now they're just covered
new_plot <- gtable_stack(g1, new_strips)
grid.newpage()
grid.draw(new_plot)
```




  * test my data
```{r, eval=FALSE, include=FALSE}
# d <- data.frame(fruit = rep(c("apple", "orange", "plum", "banana", "pear", "grape")), 
#                 farm = rep(c(0,1,3,6,9,12), each=6), 
#                 weight = rnorm(36, 10000, 2500), 
#                 size=rep(c("small", "large")))

dat <- do_isbottom %>% ungroup() %>% as.data.frame()

## Add in some colors based on the data
# dat$facet_fill_color <- c("red", "green")[dat$yes]
d <- dat %>% 
  dplyr::mutate(facet_fill_color = ifelse(is_bottom == "bottom", "red", "green"))

## Create main plot
p1 <- d %>%  
  ggplot()+
  geom_point(aes(x = DO, y = -Depth, color = Temp), show.legend = T) +
  # facet_wrap(~Date) + ## 1st submission used this line 
  # facet_grid( Date ~ is_bottom) + ## 1st revision used this line
  facet_wrap(Date ~ is_bottom, ncol = 10) +
  # scico::scale_color_scico(palette = "roma") +
  scale_color_viridis(option="inferno", direction = 1) +
  geom_vline(xintercept = 2, 'dash') +
  ylab('Sampling depth (m)') + xlab('DO (mg/l)') +
  ggtitle('DO and water temperature at different sampling depth') +
  theme_bw() +
  theme(plot.background = element_rect(fill = "transparent",colour = NA))

# p1 = ggplot(data = d, aes(x = farm, y = weight)) + 
#   geom_jitter(position = position_jitter(width = 0.3), 
#               aes(color = factor(farm)), size = 2.5, alpha = 1) + 
#   facet_wrap(~fruit)
# p1

# dummy <- ggplot(data = d, aes(x = farm, y = weight)) + 
#   facet_wrap(~fruit) + 
#   geom_rect(aes(fill=size), xmin=-Inf, xmax=Inf, ymin=-Inf, ymax=Inf, alpha = 0.5) +
#   theme_minimal()
# dummy

dummy <- p1
dummy$layers <- NULL
dummy <- dummy + 
  geom_rect(data=d, xmin=-Inf, ymin=-Inf, xmax=Inf, ymax=Inf,
            aes(fill = facet_fill_color))





library(gtable)
library(grid)

g1 <- ggplotGrob(p1)
g2 <- ggplotGrob(dummy)

gtable_select <- function (x, ...) 
{
  matches <- c(...)
  x$layout <- x$layout[matches, , drop = FALSE]
  x$grobs <- x$grobs[matches]
  x
}

panels <- grepl(pattern="panel", g2$layout$name)
strips <- grepl(pattern="strip-t", g2$layout$name)
g2$layout$t[panels] <- g2$layout$t[panels] - 1
g2$layout$b[panels] <- g2$layout$b[panels] - 1

new_strips <- gtable_select(g2, panels | strips)
grid.newpage()
grid.draw(new_strips)

gtable_stack <- function(g1, g2){
  g1$grobs <- c(g1$grobs, g2$grobs)
  g1$layout <- transform(g1$layout, z= z-max(z), name="g2")
  g1$layout <- rbind(g1$layout, g2$layout)
  g1
}
## ideally you'd remove the old strips, for now they're just covered
new_plot <- gtable_stack(g1, new_strips)
grid.newpage()
grid.draw(new_plot)
```



