---
title: "Figure2"
author: "Yingjie"
date: "10/7/2021"
output: html_document
editor_options: 
  chunk_output_type: console
---


  This script aims to combine sub-plots for Figure 2. 



# Setup 
```{r}
# remove(list = ls())

getwd()

library(tidyverse)
library(dplyr)
library(Rmisc) ## `summarySE()` provides standard deviation, standard error of the mean, and a (default 95%) confidence interval

library(ggplot2)
library(ggpubr)
library(viridis)
library(tidyquant)

source('helperFunctions.R') ## mae() function
```



# Data


## Load data from 3 models. 
  
```{r - LLR and FDA data}


## 1. load llModErr and fdaErr -----------------------------------------------------------
load(file = './data/errDat.Rdata')
names(errLag)


## --> before 2022/4/20, this data include `llModErr` and `fdaErr` seperately. Here, we need to extract these two from the 
##     updated data called `errLag`
# names(errLag)
  ## "lag"      "errType"  "mean_wse" "med_oose" "max_oose" "min_oose" "modType" 
# errDat <- errLag %>%
#   dplyr::rename_with(., ~ (gsub("_oose", "", .x, fixed = TRUE))) %>%
#   dplyr::rename(trainingSampErr = mean_wse) %>%
#   dplyr::select(lag, errType, med, max, min, everything())


## --> 4/25/2022: updated "errDat.Rdata" that includes all the 1000 replicates. 
##  there are several options to plot the uncertainty (shade band around the line plot) 
##  1. use the true min - max range
##  2. use the 95% quantiles range (to remove potential outliers?)
##  3. use confidence interval, IPCC AR6 defines >= 90% interval as the "very likely" range.



# prb <- 0       # to get the actual range (min to max)
prb <- 2.5/100 # to get 95% quantiles range
# prb <- 5/100   # to get 90% quantiles range


### error data for **testing set** -------------------------------------------------------
errDat_test <- errLag %>%
  dplyr::rename(value = error) %>%
  dplyr::filter(errType2 == "Out of Sample") %>%
  dplyr::select(-errType2) %>%
  group_by(modType, lag, errType) %>%
  slice_sample(n = 20) %>%
  dplyr::summarise(med = median(value, na.rm = T),
                   avg = mean(value, na.rm = T),
                   iqr = IQR(value, na.rm = T),
                   ## --> for the max and min, we can either use the actual max, min, or 95% quantiles range
                   # max = max(value, na.rm = T), 
                   # min = min(value, na.rm = T),
                   min = quantile(value, prb),
                   max = quantile(value, probs = 1-prb),
                   ### --> or use confidence interval ---
                   lci = CI(value, ci = 0.95)['lower'],
                   uci = CI(value, ci = 0.95)['upper']
                   # avg1 = CI(value)['mean']
                   ) %>%
  dplyr::select(modType, lag, errType, med, max, min, everything())




### error data for **training set** ------------------------------------------------------
errDat_train <- errLag %>%
  dplyr::rename(value = error) %>%
  dplyr::filter(errType2 == "Within Sample") %>%
  dplyr::select(-errType2) %>%
  group_by(modType, lag, errType) %>%
  dplyr::rename(trainingSampErr = value) %>%
  as.data.frame()

### put both in one file
errDat <- merge(errDat_test, errDat_train, by = c("modType", "lag", "errType"))



## filter out data for each model --------------------------------------------------------
llModErr <- errDat %>%
  dplyr::filter(modType == 'Lagged Linear') %>%
  dplyr::select(-modType)


fdaErr  <- errDat %>%
  dplyr::filter(modType == 'Functional Data Analysis')%>%
  dplyr::select(-modType)
```



```{r - RF data}
## 2. load RF model error data --------------------------------------------------------------------
fname <- paste0('./data/results_RF/err_rf_Day_DObottom_2014_2014.Rdata'); fname
load(fname)
##
## * This loaded file includes two data sets
##    `err_rf`:        model errors for the testing set
##    `err_rf_train`:  model errors for the training set
##



## for the testing set -------------------------------------------------------------------
acc_set <- 'testing'

### input data for plotting 
err_rf_test <- err_rf %>%
  gather(key = 'errType', value = 'value', RMSE:R2) %>%
  dplyr::mutate(errType = factor(errType, levels = c('R2', 'RMSE', 'MAE')))

### option 1. use mean, se OR sd,for plotting ----

# rfErr_test <- summarySE(data = err_rf_test, measurevar="value", groupvars=c("year", "nw", "errType")) %>%
#   dplyr::select(-year, -N) %>%
#   dplyr::rename(lag = nw)



### option 2. use median, max, min for plotting -----
rfErr_test <- err_rf_test %>%
  dplyr::select(-year) %>%
  dplyr::rename(lag = nw) %>%
  group_by(lag, errType) %>%
  slice_sample(n = 20) %>%
  dplyr::summarise(med = median(value, na.rm = T),
                   # max = max(value, na.rm = T), 
                   # min = min(value, na.rm = T), 
                   min = quantile(value, prb),
                   max = quantile(value, probs = 1-prb),
                   avg = mean(value, na.rm = T),
                   iqr = IQR(value, na.rm = T),       ## IQR = Q3-Q1 ('Interquartile Range' = 'third quartile' - 'first quartile')
                   lci = CI(value, ci = 0.95)['lower'],
                   uci = CI(value, ci = 0.95)['upper']
                   ) %>% 
  # dplyr::select(-avg, -iqr) %>% ## updated on 4/21/2022 using new data
  dplyr::mutate(trainingSampErr = NA) %>%
  dplyr::filter(lag <= 80) %>%
  as.data.frame()
  



## for the training set ------------------------------------------------------------------
## --> add within-sample-error (i.e., training accuracy) of RF model
rfErr_train <- err_rf_train %>%
  gather(key = 'errType', value = 'value', RMSE:R2) %>%
  dplyr::mutate(errType = factor(errType, levels = c('R2', 'RMSE', 'MAE'))) %>%
  dplyr::select(-year) %>%
  dplyr::rename(lag = nw) %>%
  group_by(lag, errType) %>%
  dplyr::summarise(med = median(value, na.rm = T), ## median
                   # max = max(value, na.rm = T), 
                   # min = min(value, na.rm = T), 
                   min = quantile(value, prb),
                   max = quantile(value, probs = 1-prb),
                   avg = mean(value, na.rm = T),
                   sd  = sd(value, na.rm = T),
                   iqr = IQR(value, na.rm = T)) %>%
  # dplyr::select(-avg, -iqr) %>%
  dplyr::filter(lag <=80) %>%
  as.data.frame()

## --> final RF 
rfErr_test$trainingSampErr <- rfErr_train$avg





## 3. fix and unify the data frame format ------------------------------------------------

names(fdaErr)
names(llModErr)
names(rfErr_test)

## make sure `fdaErr` is the same format as `llModErr`
# fdaErr <- fdaErr %>% 
#   dplyr::rename(errType=name, 
#                 max = upr, 
#                 min = lwr) %>%
#   dplyr::mutate(iqr = NA) %>%
#   dplyr::select(names(llModErr))



# names(fdaErr)
# fdaErr_na10 <- fdaErr %>%
#   dplyr::filter(lag < 20) %>%
#   dplyr::mutate(lag = lag - 10) %>%
#   dplyr::mutate_at(vars(med:trainingSampErr), ~replace(., is.numeric(.), NA))
#   # dplyr::mutate_at(c("med","max","min","iqr","trainingSampErr"), as.na(), na.rm = TRUE)
# 
# fdaErr <- rbind(fdaErr, fdaErr_na10)



## 4. get the complete_rate of RS band 

complete_rate <- err_rf %>%
  distinct(year, nw, complete_rate_avg) %>%
  dplyr::mutate(nw = - nw) %>%
  dplyr::rename(lag = nw)

mean(complete_rate$complete_rate_avg) ## 0.35

complete_rate %>%
  dplyr::filter(lag >= -80) %>%
  ggplot() +
  geom_line(aes(x = lag, y = complete_rate_avg), color = 'orange') +
  theme_bw()
```





## Table 1 - result summary

  This table reports the accuracy information based on best time windows (or time lag) we choose for model inputs. 
  
  For "Training error", we report the `median` values for each model and each indicator;
  
  For "Testing error",  we *additionally* report the `lower and upper percentiles`. 

```{r}
names(rfErr_test)


### for training data set ----------------------------------------------------------------

### --> 1. if look at the most recent 4 days
# rfErr_train %>%
#   ungroup() %>%
#   dplyr::filter(lag < 5) %>%
#   group_by(errType) %>%
#   # dplyr::summarise() %>%
#   arrange(errType, desc(med)) %>%
#   as.data.frame()


### --> 2. if look at the whole 80 days range
err_rf_train %>%
  gather(key = 'errType', value = 'value', RMSE:R2) %>%
  dplyr::mutate(errType = factor(errType, levels = c('R2', 'RMSE', 'MAE'))) %>%
  dplyr::select(-year) %>%
  dplyr::rename(lag = nw) %>%
  # dplyr::filter(lag < 5) %>%
  dplyr::filter(lag < 5) %>%
  group_by(errType) %>%
  dplyr::summarise(
    # med = median(value, na.rm = T), ## median
                   # max = max(value, na.rm = T), 
                   # min = min(value, na.rm = T), 
                   # min = quantile(value, prb),
                   # max = quantile(value, probs = 1-prb),
                   avg = mean(value, na.rm = T),
                   sd = sd(value, na.rm = T),
                   iqr = IQR(value, na.rm = T)) %>%
  as.data.frame()








### for testing data set -----------------------------------------------------------------
# rfErr_test %>% 
#   ungroup() %>%
#   dplyr::filter(lag < 5) %>%
#   group_by(errType) %>%
#   # dplyr::summarise() %>%
#   arrange(errType, desc(med)) %>%
#   as.data.frame()

library(plotrix)

err_rf_test %>%
  dplyr::ungroup() %>%
  dplyr::select(-year) %>%
  dplyr::rename(lag = nw) %>%
  dplyr::ungroup() %>%
  dplyr::filter(lag < 5) %>%
  dplyr::group_by(errType) %>%
  dplyr::summarise(
    # med = median(value, na.rm = T),
    # q1 = quantile(value, probs = 1/4) %>% as.numeric(),
    # q3 = quantile(value, probs = 3/4) %>% as.numeric(),
    # d1 = q1 - med,
    # d3 = q3 - med,
    avg = mean(value, na.rm = T),
    sd = sd(value, na.rm = T),
    # n  = n(),
    # lse = STDERR(value)['lower'], ## lower standard error
    # lse = STDERR(value)['upper'],
    # mse = STDERR(value)['mean'],
    # se2 = std.error(value),
    # lse2 = mse + se2,
    lci = CI(value, ci = 0.9)['lower'],
    uci = CI(value, ci = 0.9)['upper']
                   
                   ) %>% 
  dplyr::mutate(trainingSampErr = NA) %>%
  as.data.frame()


```



## Plot 3 models 

```{r}
### 1. options to plot lines -------------------------------------------------------------
# line_to_be_plot <- "med" ## use `median` values to plot the lines
line_to_be_plot <- "avg"   ## use `mean`


### 2. options to plot shade -------------------------------------------------------------
# upper = 'max'; lower = 'min'
upper = 'uci'; lower = 'lci'



### 3. range of lag to plot --------------------------------------------------------------
lag_range <- 30
lag_range <- 80
lag_range <- 60


### 4. if to plot the complete_rate of data 
complete_rate_add <- T
# complete_rate_add <- F


complete_rate_dat <- complete_rate %>% dplyr::filter(lag >= -lag_range)

if(complete_rate_add == T) {
  complete_rate_alpha <- 1
} else {
  complete_rate_alpha <- 0
}
                  



### 5. 
if_smooth <- F
# if_smooth <- T

bandwidth_smooth <- ifelse(if_smooth == T, 5, NA)




### plot ---------------------------------------------------------------------------------
model_fullname <- c('Functional Data Analysis', 'Lagged Linear Regression', 'Random Forest Regression')
model_levels   <- c('FDA', 'LLR', 'RFR')

## 1. the input data for plot
err_3models <- rbind(llModErr   %>% dplyr::mutate(mod = 'LLR'),
                     fdaErr     %>% dplyr::mutate(mod = 'FDA'),
                     rfErr_test %>% dplyr::mutate(mod = 'RFR')) %>%
  dplyr::mutate(lag = -lag) %>%
  dplyr::rename('value' = all_of(line_to_be_plot)) %>%
  dplyr::rename('upper' = all_of(upper)) %>%
  dplyr::rename('lower' = all_of(lower)) %>%
  
  dplyr::filter(lag >= -lag_range) %>%
  
  group_by(mod, errType) %>%
  # dplyr::mutate(med_avg = mean(value, rm.na = T)) %>% ## to get the mean of mean (or median) value
  ungroup() %>%
  arrange(mod, errType) %>%
  dplyr::mutate(mod     = factor(mod,     levels = model_levels, labels = model_fullname),
                errType = factor(errType, levels = c('MAE', 'RMSE', 'R2'))) %>%
  dplyr::select(lag, errType, value, everything()) %>%
  as.data.frame()


str(err_3models)

## 2. identify the best day by looking for the date with the highest model accuracy 
# err_3models_bestday <- err_3models %>% 
#   dplyr::mutate(mod = as.factor(mod), errType = as.factor(errType)) %>%
#   group_by(mod, errType) %>%
#   dplyr::mutate(best    = ifelse(errType != 'R2', min(med), max(med, na.rm = T)),
#                 bestday = ifelse(med == best, lag, NA)) %>%
#   arrange(mod, errType, med) %>%
#   # dplyr::filter(!is.na(bestday)) %>%
#   as.data.frame()




### smooth the results -------------------------------------------------------------------
err_ls <- unique(err_3models$errType) %>% as.character(); err_ls
mod_ls <- unique(err_3models$mod) %>% as.character()

err_3models_smooth <- data.frame()


for (m in mod_ls) {
  print(m)
  
  for (e in err_ls) {
    print(e)
  
    df0 <- err_3models %>% 
      ungroup() %>%
      as.data.frame() %>%
      # dplyr::mutate(mod = as.character(mod)) %>%
      dplyr::filter(mod == m) %>%
      dplyr::filter(errType == e)
    
    df1 <- ksmooth(x = df0$lag, y = df0$value, 'normal', bandwidth=bandwidth_smooth, n = nrow(df0)) %>% 
      as.data.frame() %>%
      dplyr::rename(lag = x, value = y) %>%
      left_join(x = df0 %>% dplyr::select(-value), 
                y = ., 
                by = 'lag') 
    
    err_3models_smooth <- rbind(err_3models_smooth, df1)
}
}


if (if_smooth == T) {
  err_3models_input <- err_3models_smooth
} else {
  err_3models_input <- err_3models
}








### 3. plot ------------------------------------------------------------------------------

lag_max <- max(err_3models_input$lag, na.rm = T); lag_max
lag_min <- min(err_3models_input$lag, na.rm = T); lag_min


(p <- ggplot(data = err_3models_input %>% dplyr::rename(Training = trainingSampErr), 
             aes(x=lag, y=value), size = 0.5)+
   
    # geom_line()+
    geom_point(shape = 16, size = .8, alpha = 0.3)+
    geom_line(aes(y=Training, color = 'Training'), 
              # col='red', 
              size  = 0.4,
              alpha = 0.4, linetype = 'solid', show.legend = T)+ ## 'dashed', 'dotted'
   #  labs(colour="Datasets",x="xxx",y="yyy")+
   # scale_color_manual(values = c("blue","red"))+
   # scale_color_viridis() +
    geom_line(data = complete_rate_dat, aes(x = lag, y = complete_rate_avg), color = 'orange', alpha = complete_rate_alpha) +
    # geom_ribbon(aes(ymax = upper, ymin = lower), alpha = 0.2)+
    geom_smooth(method = 'loess', span = 0.27, formula = 'y~x', linetype=1, color = 'gray40', size = 0.4) +
    
    scale_x_continuous(breaks = seq(lag_min, lag_max, 10), limits = c(lag_min, lag_max)) +
    
    ## --> To highlight the best data range for prediction  
    # geom_vline(data = err_3models_bestday,  aes(xintercept = bestday), linetype = "dashed", color="blue") + 
   geom_vline(xintercept = -30, linetype = 'dashed', alpha = 0.3) +
   geom_rect(
      # data = data.frame(mod = factor(c('Lagged Linear Regression'))), ## not to add 'rect' for FDA
      data = data.frame(mod = factor(model_fullname[1:3])), ## not to add 'rect' for FDA
      aes(x = NULL, y = NULL, xmin=lag_min,xmax=-30, ymin=-Inf, ymax=Inf),
      fill = 'gray', alpha=0.2, show.legend = F) +
    geom_rect(
      data = data.frame(mod = factor(c('Random Forest Regression'))), ## not to add 'rect' for FDA
      aes(x = NULL, y = NULL, xmin=-4,xmax=0, ymin=-Inf, ymax=Inf), 
      fill = 'blue', alpha=0.3) + 
    geom_rect(
      data = data.frame(mod = factor(c('Lagged Linear Regression', 'Random Forest Regression'))), ## not to add 'rect' for FDA
      aes(x = NULL, y = NULL, xmin=-19,xmax=-15, ymin=-Inf, ymax=Inf), 
      fill = 'blue', alpha=0.1, show.legend = F) + 
   
   # geom_hline(yintercept = 0.6, linetype = 'dashed', alpha = 0.3) +
    facet_grid(errType~mod, scales = 'free_y', switch = 'y')+
    labs(x='Time lag', y='Model Accuracy') +
   
     scale_colour_manual(name = "Legend",
                         values = c("Testing" = "black", "Training"= "red")) +
   
   
    theme_bw() +
    theme(
          legend.position = c(0.25, 0.74), ## right side: 0.92, 0.74
          legend.key=element_blank(),  ## remove the key background
          legend.key.height = unit(0.01, 'npc'),
          legend.title = element_blank(),
          legend.background = element_rect(fill='transparent'),
          legend.box.background = element_rect(fill='transparent', color = 'transparent'), 
          panel.grid.minor = element_blank())
)
# library(lemon)
# reposition_legend(p, 'left')
# ggsave('./figures/accuracy_comparison_3models80d.png', p, width=7, height=5)


fname <- paste0('./figures/accuracy_comparison_3models80d_legend', 
                '95CI_lagRange', lag_range, '_',
                rf_na.action, '_addN-', complete_rate_add,
                '0.png'); fname
ggsave(filename = fname, p, width=7, height=5)
```




```{r - plot with legend}
## 1. the input data for plot
err_3models_long <- err_3models_input %>%
  gather(key = set, value = value, c(value, trainingSampErr)) %>%
  as.data.frame() %>%
  dplyr::mutate(set = as.factor(set))

err_3models_long$set = factor(x = err_3models_long$set, levels = c('value', 'trainingSampErr'), labels = c('Testing', 'Training'))

levels(err_3models_long$mod)

lag_max <- max(err_3models_long$lag, na.rm = T); lag_max
lag_min <- min(err_3models_long$lag, na.rm = T); lag_min

### 3. plot
(p <- ggplot(data = err_3models_long, aes(x=lag, y=value))+
    
    geom_line(data = complete_rate_dat, aes(x = lag, y = complete_rate_avg), color = 'orange', alpha = complete_rate_alpha) +
    
    geom_line(aes(color = set, linetype = set), size = 0.3)+
    scale_colour_manual(values = c('black', 'red')) +
    
    # geom_point(
    #   data = err_3models_long %>% filter(set == 'Testing'),
    #   shape = 16, alpha = 0.2)+

    # scale_linetype_manual(values = c('solid', 'dashed')) +
    scale_linetype_manual(values = c('solid', 'solid')) +
    geom_ribbon(aes(ymax = upper, ymin = lower), alpha = 0.2, show.legend = F)+
    # geom_smooth(span = 0.26, formula = 'y~x', linetype=1, color = 'gray40', size = 0.5) +
    
    ## --> To highlight the best data range for prediction  
    geom_vline(xintercept = -30, linetype = 'dashed', alpha = 0.3) +
    geom_rect(
      # data = data.frame(mod = factor(c('Lagged Linear Regression'))), ## not to add 'rect' for FDA
      data = data.frame(mod = factor(model_fullname[1:3])), ## not to add 'rect' for FDA
      aes(x = NULL, y = NULL, xmin=lag_min,xmax=-30, ymin=-Inf, ymax=Inf),
      fill = 'gray', alpha=0.2, show.legend = F) +
    geom_rect(
      data = data.frame(mod = factor(c('Random Forest Regression'))), ## not to add 'rect' for FDA
      aes(x = NULL, y = NULL, xmin=-4,xmax=0, ymin=-Inf, ymax=Inf), 
      fill = 'blue', alpha=0.1, show.legend = F) + 
    geom_rect(
      data = data.frame(mod = factor(c('Lagged Linear Regression'))), ## not to add 'rect' for FDA
      aes(x = NULL, y = NULL, xmin=-19,xmax=-15, ymin=-Inf, ymax=Inf), 
      fill = 'blue', alpha=0.1, show.legend = F) + 
    facet_grid(errType~mod, scales = 'free_y', switch = "y")+
    scale_x_continuous(breaks = seq(lag_min, lag_max, 10), limits = c(lag_min, lag_max)) +
    labs(x='Time lag', y='Model Accuracy') +
    theme_bw() +
    theme(legend.position = c(0.25, 0.74), ## right side: 0.92, 0.74
          legend.key=element_blank(),  ## remove the key background
          legend.key.height = unit(0.01, 'npc'),
          legend.title = element_blank(),
          legend.background = element_rect(fill='transparent'),
          legend.box.background = element_rect(fill='transparent', color = 'transparent'), 
          panel.grid.minor = element_blank())
)

# fname <- paste0('./figures/accuracy_comparison_3models80d_legend', (1-prb*2)*100, '.png'); fname
fname <- paste0('./figures/accuracy_comparison_3models80d_legend', 
                '95CI_lagRange', lag_range, '_',
                rf_na.action, '_addN-', complete_rate_add,
                '1.png'); fname
ggsave(filename = fname, p, width=7, height=5)
```












***************************** THE END ***************************** 

**The following code was used for FDA results without testing accuracy when feeding in different time ranges data**

  Tried `mean` value too, and it looks `mean` value is easier to identify the *best day*. 
  
  --> also thinking about to highlight days with higher accuracy then the average of (medians)
  
  --> but still, no clear pattern found. So, just present the trends of `median`...
  
```{r eval=FALSE, include=FALSE}

## 1. the input data for plot
err_2models <- rbind(llModErr %>% dplyr::mutate(mod = 'LLR'),
                     rfErr_test    %>% dplyr::mutate(mod = 'RFR')) %>%
  dplyr::mutate(lag = -lag) %>%
  group_by(mod, errType) %>%
  dplyr::mutate(med_avg = mean(med, rm.na = T)) %>% ## to get the mean of median value
  ungroup() %>%
  arrange(mod, errType) %>%
  as.data.frame()



## 2. identify the best day by looking for the date with the highest model accuracy 
err_2models_bestday <- err_2models %>% 
  dplyr::mutate(mod = as.factor(mod), errType = as.factor(errType)) %>%
  group_by(mod, errType) %>%
  dplyr::mutate(best    = ifelse(errType != 'R2', min(med), max(med, na.rm = T)),
                bestday = ifelse(med == best, lag, NA)) %>%
  arrange(mod, errType, med) %>%
  # dplyr::filter(!is.na(bestday)) %>%
  as.data.frame()

### - to add the 2nd best day as well?
err_2models_bestday21 <- err_2models %>% 
  ungroup() %>%
  dplyr::filter(errType != 'R2') %>%
  dplyr::group_by(mod, errType) %>%
  arrange(mod, errType, med) %>%
  dplyr::slice(2) %>%
  dplyr::mutate(bestday = lag) %>%
  as.data.frame()

err_2models_bestday22 <- err_2models %>% 
  ungroup() %>%
  dplyr::filter(errType == 'R2') %>%
  dplyr::group_by(mod, errType) %>%
  arrange(mod, errType, desc(med)) %>%
  dplyr::slice(2) %>%
  dplyr::mutate(bestday = lag) %>%
  as.data.frame()

err_2models_bestday2 <- rbind(err_2models_bestday21, err_2models_bestday22)




### 3. plot
(p1 <- ggplot(err_2models, aes(x=lag, y=med))+
    geom_ribbon(aes(ymax=max,ymin=min),alpha=0.3)+
    # geom_line(aes(color = ifelse(med>med_avg, 1, 2)))+                  # size = ifelse(med>med_avg, 1, 0.5)
    geom_line()+
    scale_color_viridis() +
    geom_line(aes(y=trainingSampErr),col='red')+
    geom_vline(data = err_2models_bestday,  aes(xintercept = bestday), linetype = "dashed", color="blue") + 
    # geom_vline(data = err_2models_bestday2, aes(xintercept = bestday), linetype = "dashed", color="green") +  ## --> not good
    facet_grid(errType~mod, scales = 'free_y')+
    labs(x='Time lag',y='Model Accuracy') +
    theme_bw()
)
```






